\documentclass[a4paper]{article}
\usepackage[margin=0.5in]{geometry}
\usepackage{color}
\usepackage{fontawesome5}
\usepackage{bookmark}
\usepackage{hyperref}
\usepackage{ragged2e}
% \usepackage{changepage} % imported to be able to use \begin{adjustwidth}

\hypersetup{
  breaklinks=true,
  colorlinks=true,
  linkcolor=cyan,
  urlcolor=MyDarkBlue,
  pdfauthor={Frank Promise Edah},
  pdftitle={Resume}
}

\definecolor{MyDarkBlue}{rgb}{0, 0, 0.45}

%%%%%%%%%%%%%%%%%%%%%%%%%%
% Formatting parameters  %
%%%%%%%%%%%%%%%%%%%%%%%%%%

\newlength{\tabin}
\setlength{\tabin}{0em}
\newlength{\secsep}
\setlength{\secsep}{0.1cm}

\setlength{\hsize}{0.9\hsize}
\setlength{\parindent}{0in}
\setlength{\parskip}{0in}
\setlength{\itemsep}{0in}
\setlength{\topsep}{0in}
\setlength{\tabcolsep}{0in}

\definecolor{contactgray}{gray}{0.3}
\pagestyle{empty}

%%%%%%%%%%%%%%%%%%%%%%%%%%
%  Template Definitions  %
%%%%%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\doublelineunder}{\vspace{-4pt}\underline{\rule{525pt}{2pt}}\vspace{2pt}}
\newcommand{\lineunder}{\vspace*{-8pt}\\\hspace*{-6pt}\hrulefill\\\vspace*{-15pt}}
\newcommand{\name}[1]{\begin{center}\textsc{\Huge#1}\\\end{center}}
\newcommand{\position}[1]{\begin{center}\textsc{#1}\end{center}}
\newcommand{\contact}[1]{\vspace{\secsep}\begin{center}\color{contactgray}{\small#1}\end{center}}
\newcommand{\education}[4]{\vspace{\secsep}\textbf{#1\hfill#2}\\\textit{#3\hfill#4}\vspace{2\secsep}}
\newcommand{\educationwithgrade}[5]{\vspace{\secsep}\textbf{#1\hfill#2}\\\textit{#3\hfill#4}\linebreak\textbf{\textit{#5}}\vspace{2\secsep}}

\newenvironment{tabbedsection}[1]{
  \begin{list}{}{
    \setlength{\itemsep}{0pt}
    \setlength{\labelsep}{0pt}
    \setlength{\labelwidth}{0pt}
    \setlength{\leftmargin}{\tabin}
    \setlength{\rightmargin}{\tabin}
    \setlength{\listparindent}{0pt}
    \setlength{\parsep}{0pt}
    \setlength{\parskip}{0pt}
    \setlength{\partopsep}{0pt}
    \setlength{\topsep}{#1}
  }
  \item[]
}{\end{list}}


\newenvironment{nospacetabbing}{\begin{tabbing}}{\end{tabbing}\vspace{-1.2em}}

\newenvironment{resume_header}{}{\vspace{0pt}}

\newenvironment{resume_section}[1]{
  \filbreak
  \vspace{2\secsep}
  \textsc{\large#1}
  \lineunder
  \begin{tabbedsection}{\secsep}
}{\end{tabbedsection}}

\newenvironment{resume_subsection}[2]{
  \vspace{\secsep}
  \textbf{#1 \hfill #2} \\ \vspace{-10pt}
  \begin{tabbedsection}{0.5\secsep}
}{\end{tabbedsection}}


\newenvironment{subitems}{
  \renewcommand{\labelitemi}{-}
  \begin{itemize}
  \setlength{\labelsep}{1em}
}{\end{itemize}}

\newenvironment{resume_employer}[4]{
  \vspace{\secsep}
  \textbf{#1 \hfill #4} \\ 
  \textit{\small #2 #3}
  \begin{tabbedsection}{0pt}
  \begin{subitems}
}{\end{subitems}\end{tabbedsection}}


%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Start Document     %
%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\begin{resume_header}

  \name{Frank Promise Edah}
  \position{Site Reliability Engineer}
  \doublelineunder
  % \begin{adjustwidth}{-40pt}{-40pt} % used to manipulate margin
  % \end{adjustwidth} % used to manipulate margin
    \contact{
      % \faIcon{phone} (+48) XXX XXX XXX \hspace{0.5cm}
      \faIcon{envelope} \href{mailto:chiemerieezechukwu@outlook.com}{\underline{\smash{promisefrank97@yahoo.com}}}\hspace{0.5cm}
      \faIcon{map-marker-alt} Nuremberg, Germany \hspace{0.5cm}
      \faIcon{github} \href{https://github.com/Frankpromise}{\underline{\smash{Github}}} \hspace{0.5cm}
      \faIcon{linkedin} \href{https://www.linkedin.com/in/promise-edah-frank-959673159/}{\underline{\smash{LinkedIn}}}
    }
    \vspace{4\secsep}

\end{resume_header}

% \begin{resume_section}{Summary}
%   Software Developer with a degree in computer science and hands-on experience developing, deploying and debugging software solutions in the cloud.
%   Motivated and eager to take on new challenges while expanding my skill set.
% \end{resume_section}

\begin{resume_section}{Work Experience}
  \begin{resume_employer}{Site Reliability Engineer}{Gfk-An NIQ Company,}{Nuremberg, Germany}{March 2023 -- Present}
    \item Lead the integration of Kubecost across Kubernetes clusters; design automation scripts for metric extraction, streamline storage to AWS S3, orchestrate database sync, and facilitate data visualization via PowerBI dashboards.
    \item Implement Kubernetes ServiceMonitor using Helm charts to scrape metrics from a .NET application; design custom Grafana dashboards. This enhancement streamlines application debugging optimizes troubleshooting, and bolsters incident management effectiveness.
    \item Implement a Docker-based solution to test Helm chart configurations and host charts on a Nexus repository, leveraging GitLab CI for automation. This initiative significantly reduces the time required for Helm chart testing.
    \item Develop and manage an internal Kubernetes on-premises platform, serving multiple teams and enabling seamless cluster bootstrapping via an intuitive YAML configuration file, reducing time for deployment and configuration tasks.
    \item Integrate FluxCD and Helm for continuous deployment and GitOps workflows, significantly reducing deployment time and ensuring consistency across environments.
    \item Lead the implementation of a team-wide Helm chart, streamlining deployments and boosting developer efficiency through standardized and reusable configurations.
    \item Mentor team members, particularly on the topics of AWS, Kubernetes, FluxCD, and Helm usage, fostering a culture of knowledge sharing and professional growth.
  \end{resume_employer}

  \begin{resume_employer}{DevOps Engineer Intern}{Exadel,}{Warsaw, Poland}{June 2022 -- August 2022}
    \item Assisted senior DevOps engineers in configuring and maintaining cloud infrastructure on AWS.
    \item Contributed to the automation of deployment pipelines, ensuring swift and reliable software releases.
    \item Drafted and revised scripts in Bash and Python to automate routine tasks, enhancing operational efficiency.
    \item Participated in training sessions and workshops to stay updated on the latest DevOps tools and practices.
    % \item Designed and implemented new features for a multi component backend platform hosted on AWS to manage and monitor energy related IoT devices
    % \item Analyzed solutions and architectures to allow releases without downtime within a distributed serverless IoT platform
  \end{resume_employer}
\end{resume_section}

% \begin{resume_section}{Personal Projects}

%   \begin{resume_subsection}{Python Project Management Library}{October 2021 -- Present}
%     \begin{subitems}
%       \item Designed and implemented a python library with several classes to model project management activities and objects. \href{https://github.com/chiemerieezechukwu/project-management}{github.com/chiemerieezechukwu/project-management}
%     \end{subitems}
%   \end{resume_subsection}

%   \begin{resume_subsection}{Chat Web App}{July 2020}
%     \begin{subitems}
%       \item Used vanilla Javascript, CSS, Flask templating engine (Jinja2) to set up a fully responsive frontend and Flask, Flask-SocketIO,
%       PostgreSQL for the backend. \href{https://github.com/chiemerieezechukwu/Flask-Chat--Flask-socketio-}{github.com/chiemerieezechukwu/Flask-Chat--Flask-socketio-}
%     \end{subitems}
%   \end{resume_subsection}

% \end{resume_section}

\begin{resume_section}{Skills}
  \begin{nospacetabbing}
    \textbf{Technical Skills} \= \hspace{2em} \= AWS, Python, Bash, Git, Docker, Kubernetes, Helm, FluxCD, Terraform\\\> \> Pulumi, OpenSearch, Grafana, Prometheus, GitlabCI, GithubActions\\*
    % \textbf{Cloud Technologies} \> \> AWS Lambda, S3, DynamoDB, EC2, EKS, ECS, Cloudformation, Terraform, Pulumi\\*
    \textbf{Languages} \> \> Proficient in English; Fluent in Italian\\*
    \textbf{Other Skills} \> \> Teamwork, Problem Solving, Agile frameworks, Microsoft Project, \LaTeX\\*
  \end{nospacetabbing}
\end{resume_section}

\begin{resume_section}{Education}
  \educationwithgrade{School Of Business And Management}{October 2020 -- November 2022}{M.Sc. Business Administration}{Turin, Italy}{Final Grade: 104/110}

  \educationwithgrade{School Of Business And Management}{September 2017 -- June 2020}{B.Sc. Business And Management}{Turin, Italy}{Final Grade: 97/110}
\end{resume_section}

\begin{resume_section}{Certifications}
  \begin{subitems}
    \item \href{https://www.credly.com/earner/earned/badge/f57b9d96-2c03-45dd-bdd2-95b0f464f791}{KCNA: Kubernetes and Cloud Native Associate} \hfill August 2023
    \item \href{https://www.credly.com/earner/earned/badge/2b82f982-3f60-455c-82a4-082679866c3d}{AWS Certified Developer Associate} \hfill January 2023
    \item \href{https://www.credly.com/badges/26043bb9-cca6-4c6c-80ae-51a4ef85da84}{HashiCorp Certified: Terraform Associate} \hfill December 2022
    \item \href{}{Software Engineering (Nano Degree)} \hfill September 2022
    \item \href{https://www.credly.com/earner/earned/badge/1751ff0d-b1f8-4eee-993f-98766dc6ccea}{AWS Certified Solutions Architect -- Associate (SAA)} \hfill October 2022
    \item \href{https://cs.lpi.org/caf/Xamman/certification/verify/LPI000527039/yt3tc4dc54}{Linux Professional Institute: Linux Essentials} \hfill June 2022
    \item \href{https://www.credly.com/earner/earned/badge/fe5ff96d-d745-4a2e-a2a7-a88d49875938}{AWS Certified Cloud Practitioner (CLF)} \hfill October 2021
  \end{subitems}
\end{resume_section}

\end{document}